---
name: Armando
surname: Ocampo
position: "Data Scientist - General Practitioner - Ms Biochemistry"
address: "Universidad Autónoma del Estado de Morelos, Universidad Nacional Autónoma de México"
phone: +52 735 206 6804
email: "armando.odelvalle19@gmail.com"
github: armandoODV19
linkedin: Armando Ocampo del Valle
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::moderncv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# Work experience

 * 2018-2019 Professor of mathematics and statistics.
 * 2020-2022 General Practitioner.
 * 2022 Data analyst & Data scientists, Universidad Autónoma del Estado de Morelos.

# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "General Practitioner", "2012-2019", "Universidad Autonoma del Estado de Morelos", "Morelos, Mexico",
  "Master of Biochemistry", "2020-2022", "Universidad Nacional Autonoma de Mexico", "Morelos, Mexico"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

# Nobel Prizes

```{r}
tribble(
  ~Year, ~Type, ~Desc,
  1903, "Physics", "Awarded for her work on radioactivity with Pierre Curie and Henri Becquerel",
  1911, "Chemistry", "Awarded for the discovery of radium and polonium"
) %>% 
  brief_entries(
    glue::glue("Nobel Prize in {Type}"),
    Year, 
    Desc
  )
```

# Publications

```{r}
library(dplyr)
knitr::write_bib(c("vitae", "tibble"), "packages.bib")

bibliography_entries("packages.bib") %>%
  arrange(desc(author$family), issued)
```

# Some stuff about me

 * I poisoned myself doing research.
 * I was the first woman to win a Nobel prize
 * I was the first person and only woman to win a Nobel prize in two different sciences.
