---
name: Armando
surname: Ocampo
position: "Data Analyst - General Practitioner - Ms Biochemistry"
address: "Universidad Autónoma del Estado de Morelos, Universidad Nacional Autónoma de México"
phone: +52 735 206 6804
email: "armando.odelvalle19@gmail.com"
github: ArmandoODV19
linkedin: Armando Ocampo del Valle
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::moderncv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# Work experience

 * 2021-2022 Data analyst & management of projects in the health and nutrition area, 
Systems Biology and Translational Medicine Laboratory
 * 2019-2021 General practitioner.
 * 2018-2019 High school professor of mathematics and statistics.
 

# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Current Master of Analysis and Visualization of Big Data Student", "2022", "Universidad Internacional de la Rioja", "Mexico",
  "Data Analyst Certification", "2022", "DataCamp", "United States of America",
  "Master of Biochemistry", "2020-2022", "Universidad Nacional Autonoma de Mexico", "Morelos, Mexico",
  "General Practitioner", "2012-2019", "Universidad Autonoma del Estado de Morelos", "Obtaining degree by honorable mention for the thesis “Study of the relationship, structure, 
and function of integral proteins in platelet membranes and their influence on the 
development of atherosclerosis in early stages; an analysis by molecular dynamics. Morelos, Mexico"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```


# Some stuff about me

 * 2022 Article co-author: *Long COVID in patients with rheumatologic disease: A single center observational study*, 
DOI: 10.4103/injr.injr_118_22
 * Languages: Spanish (native speaker), English (fluent speaker).
 * Programming languages: R, SQL, Python.
 * Experience working with JSON and CSV data sets
 * Excel & Tableau project management
